---
title: "Welcome to Intro Data Science"
subtitle: "Example presentation"
date: "August 29, 2022"
footer: "[🔗 rstudio-conf-2022.github.io/teach-ds-course-website](https://rstudio-conf-2022.github.io/teach-ds-course-website)"
logo: "images/logo.png"
format: 
  revealjs:
    theme: default
    transition: fade
    slide-number: true
    incremental: false 
    chalkboard: true
    center: true
execute:
  freeze: auto
  echo: true
filters:
  - section-bibliographies
bibliography: Slides01.bib
reference-section-title: References
citeproc: false
---

# Welcome!

## Bullet point list

[@wright2015]

**Unordered**

-   Item A
-   Item B
-   Item C

**Ordered**

1.  Item 1
2.  Item 2
3.  Item 3

## Incremental list

::: incremental
-   Item 1
-   Item 2
-   Item 3
:::

## Equations

Write mathematical symbols and equations using Latex.

## Code

## Images

![Artwork by
[\@allison_horst](https://www.allisonhorst.com/)](images/penguins.png){fig-alt="Three penguins labeled Chinstrap, Gentoo, and Adelie."
fig-align="center"}

## Columns

::: columns
::: {.column width="50%"}
Calculate the proportion of penguins from each species.
:::

::: {.column width="50%"}
```{r}
#| echo: true


```
:::
:::

## Panels

::: panel-tabset
## Plot

```{r}


```

## Code

```{r}
#| echo: true
#| eval: false


```
:::

## Themes

Customize the appearance of the slides using

-   Built-in [Reveal
    theme](https://quarto.org/docs/presentations/revealjs/themes.html#using-themes)

-   Modify built-in theme using
    [Sass](https://quarto.org/docs/presentations/revealjs/themes.html#creating-themes)

    -   Variant of CSS that supports variables and other features

-   Create custom thing using Sass

Specify the theme and/or Sass file (.scss) in the YAML
